On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals

### 2019-05-09 manuscripts/IEEE/final_submission.tex
my changes
complete manu draft

We close with some remaining open challenges.  First, there is the basic problem of proving optimal lower bounds on sufficient sample size for uniqueness and stability in sparse coding.  Additionally, given the NP-hardness of verifying the spark condition for matrices, is approximating a solution to Prob.~\ref{InverseProblem} or \ref{OptimizationProblem} also computationally hard?  Finally, as $\ell_1$ relaxations for inferring sparse vectors have, in many cases, the same solutions as for $\ell_0$, is there an $\ell_1$ version of Thm.~\ref{SLCopt}? In what special cases is it efficient to check that a solution to the problems is optimal? [*** Incorporate this open problem with more words ***]

>>>>

We close with some remaining open challenges.  First, there is the basic problem of proving optimal lower bounds on sufficient sample size for uniqueness and stability in sparse coding.  Additionally, given the NP-hardness of verifying the spark condition for matrices, is approximating a solution to Prob.~\ref{InverseProblem} or \ref{OptimizationProblem} also computationally hard?  Finally, as $\ell_1$ relaxations for inferring sparse vectors have, in many cases \cite{eldar2012compressed}, the same solutions as for $\ell_0$, is there an $\ell_1$ version of Thm.~\ref{SLCopt}? In what special cases is it efficient to check that a solution to the problems is optimal? % [*** Incorporate this open problem with more words ***]
